# About {orientation="rows" scrolling="false"}

## About {height=20%}

::: {.card title="About"}
The CCP Global PQD Quarterly Trends Report provides an overview of the risk management provided by
CCPs across the globe. It complements existing public statistics, such as the BIS derivatives statistics, by
providing a summary of key indicators which provides market participants an overview of the CCP
ecosystem. The publication underlines the scope and scale of risk mitigation provided by central clearing:

  -  CCPs exposure to credit risk is collateralized through high-quality and liquid collateral;
  -  CCPs risk-manage their clearing exposure by collecting mark-to-market losses through regular variation margin (or similar) payments.

This CCP Global PQD Quarterly Trends Report helps to inform market participants, authorities, and the
general public of key features, the scale and nature of financial market infrastructure risk management.
The data is aggregated directly from the CCPs themselves according to the CCP Global standardized
template, carrying information stipulated in global regulatory guidance. Further details for individual
CCPs can be found in links provided on the [CCP Global website](https://ccp-global.org) and page 23 of this report.
:::

## Disclaimer {height=15%}
::: {.card title="Disclaimer"}
The information and analysis detailed throughout this PQD QTR are for general information 
purposes only. While we attempt to keep the information up-to-date and accurate, there are no 
representations or warranties, expressed or implied, about the completeness, accuracy, 
reliability, suitability or availability with respect to the information, or related graphics 
contained in this report. This PQD QTR may not be reproduced or redistributed, in whole or in 
part, without the written permission of CCP Global. The information contained herein does not 
substitute as investment advice and should not be relied upon for such purposes. CCP Global 
accepts no liability for any loss arising from any action taken as a result of any information 
within this report.
:::

## Etc {height=65%}

```{r}
htmlOutput("frame_test")
```

```{r}
#| context: server
output$frame_test <- renderUI({
  src="https://ccp-global.org/ccpg-pqd-dashboard/?fullscreen=1"  
  height = "900"
  toolbar="hidden" 
  unrestrictedembedding="true"
  style ="height: 100vh;"
  token="eyJraWQiOiJlYTlkYjQwMi1mZjA5LTQyMmYtYTAwMS00MmExZTQ3ZTA0NjAiLCJpc3MiOiIxNGRhNTE3Y
i0xNzRiLTQxNDAtYjBhOS1mZTI1MmNlNGFmNDgiLCJhbGciOiJIUzI1NiIsInR5cCI6IkpXVCJ9.
eyJpc3MiOiIxNGRhNTE3Yi0xNzRiLTQxNDAtYjBhOS1mZTI1MmNlNGFmNDgiLCJleHAiOjE3MTA4Mjc4MzUsImp0
aSI6ImRmMzUyMzNlLWQwMDgtNDQ2NS04YzE0LWMwMzc4MGYwZTFlNSIsImF1ZCI6InRhYmxlYXUiLCJzdWIiOiJy
aXNoaS5uYWdhckBjY3AxMi5vcmciLCJzY3AiOlsidGFibGVhdTp2aWV3czplbWJlZCIsInRhYmxlYXU6bWV0cmlj
czplbWJlZCJdfQ.4dgPEFom1O0lT7mt16k1UbzIl5hSFJ4qF7alJlfPreI" 
  ui_lnk <- tags$iframe(src = src,  scrolling="no", toolbar = toolbar, unrestrictedembedding = unrestrictedembedding, style = style, token = token)
  ui_lnk
})
```



